---
title: "Introduction to reportr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to reportr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# reportr

<!-- badges: start -->
<!-- badges: end -->

The goal of reportr is to isolate and eliminate potential outliers as you perform data analysis.

## Installation

You can install the development version of reportr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ADC-405-S26/reportr")
```

Then load reportr by using the library function:

```{r example}
library(reportr)
```

#### lin_out

Description: lin_out is a function designed to mathematically locate potential outliers in numerical datasets with one predictor x and one response variable y. As a data scientist, it can be difficult to make that distinction or find reasonable justification to do so. lin_out implements linear regression with a degree of your choosing in order to calculate the vertical distance of points from the predicted value (obtained without including the data point in question). This could be a good metric for isolating outliers and improving model performance for a regression problem.

Usage: lin_out uses linear regression on one numeric predictor and one numeric feature, with whatever degree you wish. It will return a table of each data point's vertical distance from the predicted value.

```{r}
lin_out(y = toy_data$y1, x = toy_data$x1, deg = 2)
```


#### log_out Example

Description: log_out is also designed to locate potential outliers via calculating a vertical distance column, but this implements a logistic regression model, for when the response variable y is a binomial categorical variable and predictor x is numeric. This function can be especially useful when looking for ways to improve a model's performance in a classification problem.

Usage: log_out uses logistic regression on one numeric predictor column and one binomial categorical response column. Be sure to not only define a degree, but also positive, a.k.a. which category will be treated as a response of 1 rather than 0. log_out will return a table of each data point's vertical distance from the predicted probability.

```{r}
log_out(y = toy_data$y2, x = toy_data$x1, deg = 1, positive = "TRUE")
```


#### kick_out Example

Description: lin_out and log_out are preliminary functions that obtain vertical distances and give the data scientist insight, but kick_out gets the rest of the job done. It isolates data points based on a threshold you set for the vertical distance, and will filter out the respective rows in your raw dataset to make a clean, outlier-free data frame. Be careful however, the dataset you put in kick_out must not have any missing entries, or an error will be thrown.

If you want, reportr can help eliminate those pesky outliers from your data. Add the dataset you used as a dataframe, along with the distances obtained from lin_out or log_out, and a threshold for what distances will be considered outliers to be eliminated. The result will be your dataset with all the isolated outliers filtered out (Note that the row numbers on this output can be misleading, there are actually only 13 rows here). 

```{r}
output <- log_out(y = toy_data$y2, x = toy_data$x1, deg = 1, positive = "TRUE")
kick_out(data = toy_data, distances = output$Distance, threshold = 0.7)
```

